Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-11 paper/paper.tex
Abstract and some more discussion on confidence

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\todo{Dom: The abstract goes here.}
\end{abstract}

@@

The average participant was 33.7 years old.
26 participants self-identified as male and 8 as female.
All participants reported that they had no technical problems with the study procedures.
Only 11\% of our participants said they are not with all of these visualization types: barcharts, scatterplots, and heatmaps.
On average participants spent 8 minutes on the study with 3:20 minutes standard deviation.
As expected, most participants spent more time on the questions than the visualizations and overall the most time on the questions about the precise data.

@@

@@

\todo{Dom: more threats}

@@

In future work, we should focus of usable methods to reduce the bias that can be used by approximate visualization tools.
Future work should also investigate how the findings from this paper generalize to other applications.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Data analysts often have to work with an approximate model before more precise results are available.
However, after they have seen the accurate results, are they still biased by the approximation?
In this paper we present a controlled experiment with 34 participants on Mechanical Turk to investigate whether exposure to approximate results biases user's recollection of the precise data.
In our study, we aimed to simulate an exploratory data analysis session with an approximate query processing (AQP) system, a common class of systems used to accelerate data exploration.
Our goal was to understand whether analysts are biased by approximate data and whether highlighting the difference reduces this bias.
We found that analyst's recollection of precise data is biased but have no conclusive results about whether highlighting differences reduces the bias.
The results from this paper are relevant for AQP systems and count extend to other applications in journalism and science.
\end{abstract}

@@

The average participant was 33.7 years old.
26 participants self-identified as male and 8 as female.
All participants reported that they had no technical problems with the study procedures.
Only 11\% of our participants said they are not with all of these visualization types: bar charts, scatter plots, and heatmaps.
On average participants spent 8 minutes on the study with 3:20 minutes standard deviation.
As expected, most participants spent more time on the questions than the visualizations and overall the most time on the questions about the precise data.

@@

Because errors in the responses from participants were so large, we have little statistical power to tease apart how highlighting differences may reduce biases to answer RQ2.
With more statistical power we might also be able to understand the role of how certain participants were in their responses.
For each question we asked participants to rate their confidence in their answer.
For an analyst it would be fatal to have a large bias and high confidence in their recollection.
However, if either the bias is low or the confidence is low, the analysts is likely to not make the wrong decision when it really matters.
In our data we did not see significant support for the hypothesis that high confidence correlates with lower biases.

@@

@@

In future work, we should focus of usable methods to reduce the bias that can be used by approximate visualization tools.
Also, we should also try to understand the relationship between confidence and bias to avoid that analysts make wrong decisions with high confidence.
Future work should also investigate how the findings from this paper generalize to other applications.
